### 2019-08-15 report/chapter02.Rnw
Update thesis

Simulations in \citealp{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citealp{limitmeta.2}. From the formulas above, it becomes clear that is has a larger standard error. The results of the simulation furthermore emphasize that adjustment is more reliable when effects of publication bias are strong within a meta-analysis. When no publication bias affects the meta-analysis, and event rates are low, the method provided biased estimates and the mean squared error was large. The coverage of the confidence intervals was always larger or equal to meta-analysis. It outperforms or is equal to classical meta-analysis estimates with respect to coverage, mean squared error and bias if there is publication bias, especially if event rates in the control group are small.

@@

$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}-value. Note that the test is very similar to Egger's small study effect test when $\tau^2 = 0$.\\
In practice one can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process, and how the choice of the parameters affect the evidence for remaining publication bias (selection). \citealp{limitmeta} used the method in a simulation for inference purposes, and have implemented it in the \citealp{meta.package}. However, in the simulations, the method was outperformed by the regression adjustment method when publication bias was present. Especially when event rates in the control group were small and publication bias was strong, bias, mean squared error and coverage was substantially worse. Other authors argue that selection models should in general not be used for inference (\eg \citealp{selection.assessment}).\\
The procedure in \citealp{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied. If all obtained $p$\hspace{0.4mm}-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained. If none of the $p$\hspace{0.4mm}-values is above the threshold, a wider range of values for $(a,b)$ is used. When some $p$\hspace{0.4mm}-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the pair of $a$ and $b$ that implies the fewest publication bias is chosen).\\
Currently, there is no test to detect miss-specifications in the model itself and the authors themselves have argued that a non-parametric test of the residuals would lack power.

@@

The factor $\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation. The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$. \\
The Pearson's correlation coefficient can be attained by the formulas (\citealp{olkin1985dtor}, \cite[48]{Intro.meta})

>>>>

Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citet{limitmeta.2}. From the formulas above, it becomes clear that is has a larger standard error. The results of the simulation furthermore emphasize that adjustment is more reliable when effects of publication bias are strong within a meta-analysis. When no publication bias affects the meta-analysis, and event rates are low, the method provided biased estimates and the mean squared error was large. The coverage of the confidence intervals was always larger or equal to meta-analysis. It outperforms or is equal to classical meta-analysis estimates with respect to coverage, mean squared error and bias if there is publication bias, especially if event rates in the control group are small.

@@

$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}~-~value. Note that the test is very similar to Egger's small study effect test when $\tau^2 = 0$.\\
In practice one can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process, and how the choice of the parameters affect the evidence for remaining publication bias (selection). \citet{limitmeta} used the method in a simulation for inference purposes, and have implemented it in the \citet{meta.package}. However, in the simulations, the method was outperformed by the regression adjustment method when publication bias was present. Especially when event rates in the control group were small and publication bias was strong, bias, mean squared error and coverage was substantially worse. Other authors argue that selection models should in general not be used for inference (\eg \citealp{selection.assessment}).\\
The procedure in \citet{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied. If all obtained  $p$\hspace{0.4mm}~-~values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained. If none of the  $p$\hspace{0.4mm}~-~values is above the threshold, a wider range of values for $(a,b)$ is used. When some  $p$\hspace{0.4mm}~-~values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the pair of $a$ and $b$ that implies the fewest publication bias is chosen).\\
Currently, there is no test to detect miss-specifications in the model itself and the authors themselves have argued that a non-parametric test of the residuals would lack power.

@@

The factor $\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation. The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $\se_d^2$. \\
The Pearson's correlation coefficient can be attained by the formulas (\citealp{olkin1985dtor}, \cite[48]{Intro.meta})
